---
title: "AdvancedAnalysis"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{AdvancedAnalysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# 4. Advanced Analysis
## 4.1 trend_plot
Trend plot for visualizing gene expression trend profile in multiple traits.
```{r trend_plot, warning=FALSE}
library(TOmicsVis)

# 1. Load chord_data example datasets
data(trend_data)

# 2. Run trend_plot plot function
trend_plot(
  trend_data,
  scale_method = "globalminmax",
  miss_value = "exclude",
  line_alpha = 0.5,
  show_points = TRUE,
  show_boxplot = TRUE,
  num_column = 2,
  xlab = "Traits",
  ylab = "Genes Expression",
  sci_fill_color = "Sci_AAAS",
  sci_fill_alpha = 0.8,
  sci_color_alpha = 0.8,
  legend_pos = "right",
  legend_dir = "vertical",
  ggTheme = "theme_light"
)
```

Get help using command `?TOmicsVis::trend_plot` or reference page [https://benben-miao.github.io/TOmicsVis/reference/trend_plot.html](https://benben-miao.github.io/TOmicsVis/reference/trend_plot.html).
```{r}
# Get help with command in R console.
# ?TOmicsVis::trend_plot
```

## 4.2 wgcna_pipeline
WGCNA analysis pipeline for RNA-Seq.
```{r wgcna_pipeline, warning=FALSE}
# 1. Load wgcna_pipeline example datasets
data(wgcna_gene_exp)
data(wgcna_sample_group)

# 2. Run wgcna_pipeline plot function
# wgcna_pipeline(wgcna_gene_exp, wgcna_sample_group)
```

Get help using command `?TOmicsVis::wgcna_pipeline` or reference page [https://benben-miao.github.io/TOmicsVis/reference/wgcna_pipeline.html](https://benben-miao.github.io/TOmicsVis/reference/wgcna_pipeline.html).
```{r}
# Get help with command in R console.
# ?TOmicsVis::wgcna_pipeline
```

## 4.3 network_plot
Network plot for analyzing and visualizing relationship of genes.
```{r network_plot, warning=FALSE}
# 1. Load example datasets
data(network_data)
head(network_data)

# 2. Run network_plot plot function
network_plot(
  network_data,
  calcBy = "degree",
  degreeValue = 0.05,
  nodeColorNormal = "#00888888",
  nodeBorderColor = "#FFFFFF",
  nodeColorFrom = "#FF000088",
  nodeColorTo = "#00880088",
  nodeShapeNormal = "circle",
  nodeShapeSpatial = "csquare",
  nodeSize = 10,
  labelSize = 0.5,
  edgeCurved = TRUE,
  netLayout = "layout_on_sphere"
)
```

Get help using command `?TOmicsVis::network_plot` or reference page [https://benben-miao.github.io/TOmicsVis/reference/network_plot.html](https://benben-miao.github.io/TOmicsVis/reference/network_plot.html).
```{r}
# Get help with command in R console.
# ?TOmicsVis::network_plot
```
