---
title: "GOandKEGG"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{GOandKEGG}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# 5. GO and KEGG Enrichment
## 5.1 chord_plot
Chord plot for visualizing the relationships of pathways and genes.
```{r chord_plot, warning=FALSE}
library(TOmicsVis)

# 1. Load chord_data example datasets
data(chord_data)

# 2. Run chord_plot plot function
chord_plot(
  chord_data,
  multi_colors = "RainbowColors",
  color_alpha = 0.5,
  link_visible = TRUE,
  link_dir = -1,
  link_type = "diffHeight",
  sector_scale = "Origin",
  width_circle = 3,
  dist_name = 3,
  label_dir = "Vertical",
  dist_label = 0.3
)
```

Get help using command `?TOmicsVis::chord_plot` or reference page [https://benben-miao.github.io/TOmicsVis/reference/chord_plot.html](https://benben-miao.github.io/TOmicsVis/reference/chord_plot.html).
```{r}
# Get help with command in R console.
# ?TOmicsVis::chord_plot
```

## 5.2 go_enrich
GO enrichment analysis based on GO annotation results (None/Exist Reference Genome).
```{r go_enrich, warning=FALSE}
# 1. Load example datasets
data(go_anno)
head(go_anno)

data(go_deg_fc)
head(go_deg_fc)

# 2. Run go_enrich analysis function
res <- go_enrich(
  go_anno,
  go_deg_fc,
  padjust_method = "fdr",
  pvalue_cutoff = 0.5,
  qvalue_cutoff = 0.5
)
head(res)
```

Get help using command `?TOmicsVis::go_enrich` or reference page [https://benben-miao.github.io/TOmicsVis/reference/go_enrich.html](https://benben-miao.github.io/TOmicsVis/reference/go_enrich.html).
```{r}
# Get help with command in R console.
# ?TOmicsVis::go_enrich
```

## 5.3 go_enrich_stat
GO enrichment analysis and stat plot based on GO annotation results (None/Exist Reference Genome).
```{r go_enrich_stat, warning=FALSE}
# 1. Load example datasets
data(go_anno)
# head(go_anno)

data(go_deg_fc)
# head(go_deg_fc)

# 2. Run go_enrich_stat analysis function
go_enrich_stat(
  go_anno,
  go_deg_fc,
  padjust_method = "fdr",
  pvalue_cutoff = 0.5,
  qvalue_cutoff = 0.5,
  max_go_item = 15,
  strip_fill = "#CDCDCD",
  xtext_angle = 45,
  sci_fill_color = "Sci_AAAS",
  sci_fill_alpha = 0.8,
  ggTheme = "theme_light"
)
```

Get help using command `?TOmicsVis::go_enrich_stat` or reference page [https://benben-miao.github.io/TOmicsVis/reference/go_enrich_stat.html](https://benben-miao.github.io/TOmicsVis/reference/go_enrich_stat.html).
```{r}
# Get help with command in R console.
# ?TOmicsVis::go_enrich_stat
```

## 5.4 go_enrich_bar
GO enrichment analysis and bar plot based on GO annotation results (None/Exist Reference Genome).
```{r go_enrich_bar, warning=FALSE}
# 1. Load example datasets
data(go_anno)
# head(go_anno)

data(go_deg_fc)
# head(go_deg_fc)

# 2. Run go_enrich_bar analysis function
go_enrich_bar(
  go_anno,
  go_deg_fc,
  padjust_method = "fdr",
  pvalue_cutoff = 0.5,
  qvalue_cutoff = 0.5,
  sign_by = "p.adjust",
  category_num = 30,
  font_size = 12,
  low_color = "#ff0000aa",
  high_color = "#008888aa",
  ggTheme = "theme_light"
)
```

Get help using command `?TOmicsVis::go_enrich_bar` or reference page [https://benben-miao.github.io/TOmicsVis/reference/go_enrich_bar.html](https://benben-miao.github.io/TOmicsVis/reference/go_enrich_bar.html).
```{r}
# Get help with command in R console.
# ?TOmicsVis::go_enrich_bar
```

## 5.5 go_enrich_dot
GO enrichment analysis and dot plot based on GO annotation results (None/Exist Reference Genome).
```{r go_enrich_dot, warning=FALSE}
# 1. Load example datasets
data(go_anno)
# head(go_anno)

data(go_deg_fc)
# head(go_deg_fc)

# 2. Run go_enrich_dot analysis function
go_enrich_dot(
  go_anno,
  go_deg_fc,
  padjust_method = "fdr",
  pvalue_cutoff = 0.5,
  qvalue_cutoff = 0.5,
  sign_by = "p.adjust",
  category_num = 30,
  font_size = 12,
  low_color = "#ff0000aa",
  high_color = "#008888aa",
  ggTheme = "theme_light"
)
```

Get help using command `?TOmicsVis::go_enrich_dot` or reference page [https://benben-miao.github.io/TOmicsVis/reference/go_enrich_dot.html](https://benben-miao.github.io/TOmicsVis/reference/go_enrich_dot.html).
```{r}
# Get help with command in R console.
# ?TOmicsVis::go_enrich_dot
```

## 5.6 go_enrich_tree
GO enrichment analysis and tree plot based on GO annotation results (None/Exist Reference Genome).
```{r go_enrich_tree, warning=FALSE}
# 1. Load example datasets
data(go_anno)
# head(go_anno)

data(go_deg_fc)
# head(go_deg_fc)

# 2. Run go_enrich_tree analysis function
go_enrich_tree(
  go_anno,
  go_deg_fc,
  padjust_method = "fdr",
  pvalue_cutoff = 0.5,
  qvalue_cutoff = 0.5,
  sign_by = "p.adjust",
  category_num = 20,
  font_size = 4,
  low_color = "#ff0000aa",
  high_color = "#008888aa",
  hclust_method = "complete",
  ggTheme = "theme_light"
)
```

Get help using command `?TOmicsVis::go_enrich_tree` or reference page [https://benben-miao.github.io/TOmicsVis/reference/go_enrich_tree.html](https://benben-miao.github.io/TOmicsVis/reference/go_enrich_tree.html).
```{r}
# Get help with command in R console.
# ?TOmicsVis::go_enrich_tree
```

## 5.7 go_enrich_net
GO enrichment analysis and net plot based on GO annotation results (None/Exist Reference Genome).
```{r go_enrich_net, warning=FALSE}
# 1. Load example datasets
data(go_anno)
# head(go_anno)

data(go_deg_fc)
# head(go_deg_fc)

# 2. Run go_enrich_net analysis function
# go_enrich_net(
#   go_anno,
#   go_deg_fc,
#   padjust_method = "fdr",
#   pvalue_cutoff = 0.5,
#   qvalue_cutoff = 0.5,
#   category_num = 20,
#   net_layout = "circle",
#   net_circular = TRUE,
#   low_color = "#ff0000aa",
#   high_color = "#008888aa"
# )
```

Get help using command `?TOmicsVis::go_enrich_net` or reference page [https://benben-miao.github.io/TOmicsVis/reference/go_enrich_net.html](https://benben-miao.github.io/TOmicsVis/reference/go_enrich_net.html).
```{r}
# Get help with command in R console.
# ?TOmicsVis::go_enrich_net
```

## 5.8 kegg_enrich
KEGG enrichment analysis based on KEGG annotation results (None/Exist Reference Genome).
```{r kegg_enrich, warning=FALSE}
# 1. Load example datasets
data(kegg_anno)
head(kegg_anno)

data(kegg_deg_fc)
head(kegg_deg_fc)

# 2. Run go_enrich analysis function
res <- kegg_enrich(
  kegg_anno,
  kegg_deg_fc,
  padjust_method = "fdr",
  pvalue_cutoff = 1,
  qvalue_cutoff = 1
)
head(res)
```

Get help using command `?TOmicsVis::kegg_enrich` or reference page [https://benben-miao.github.io/TOmicsVis/reference/kegg_enrich.html](https://benben-miao.github.io/TOmicsVis/reference/kegg_enrich.html).
```{r}
# Get help with command in R console.
# ?TOmicsVis::kegg_enrich
```

## 5.9 kegg_enrich_bar
KEGG enrichment analysis and bar plot based on KEGG annotation results (None/Exist Reference Genome).
```{r kegg_enrich_bar, warning=FALSE}
# 1. Load example datasets
data(kegg_anno)
# head(kegg_anno)

data(kegg_deg_fc)
# head(kegg_deg_fc)

# 2. Run kegg_enrich_bar analysis function
kegg_enrich_bar(
  kegg_anno,
  kegg_deg_fc,
  padjust_method = "fdr",
  pvalue_cutoff = 1,
  qvalue_cutoff = 1,
  sign_by = "p.adjust",
  category_num = 30,
  font_size = 12,
  low_color = "#ff0000aa",
  high_color = "#008888aa",
  ggTheme = "theme_light"
)
```

Get help using command `?TOmicsVis::kegg_enrich_bar` or reference page [https://benben-miao.github.io/TOmicsVis/reference/kegg_enrich_bar.html](https://benben-miao.github.io/TOmicsVis/reference/kegg_enrich_bar.html).
```{r}
# Get help with command in R console.
# ?TOmicsVis::kegg_enrich_bar
```

## 5.10 kegg_enrich_dot
KEGG enrichment analysis and dot plot based on KEGG annotation results (None/Exist Reference Genome).
```{r kegg_enrich_dot, warning=FALSE}
# 1. Load example datasets
data(kegg_anno)
# head(kegg_anno)

data(kegg_deg_fc)
# head(kegg_deg_fc)

# 2. Run kegg_enrich_dot analysis function
kegg_enrich_dot(
  kegg_anno,
  kegg_deg_fc,
  padjust_method = "fdr",
  pvalue_cutoff = 1,
  qvalue_cutoff = 1,
  sign_by = "p.adjust",
  category_num = 30,
  font_size = 12,
  low_color = "#ff0000aa",
  high_color = "#008888aa",
  ggTheme = "theme_light"
)
```

Get help using command `?TOmicsVis::kegg_enrich_dot` or reference page [https://benben-miao.github.io/TOmicsVis/reference/kegg_enrich_dot.html](https://benben-miao.github.io/TOmicsVis/reference/kegg_enrich_dot.html).
```{r}
# Get help with command in R console.
# ?TOmicsVis::kegg_enrich_dot
```

## 5.11 kegg_enrich_tree
KEGG enrichment analysis and tree plot based on KEGG annotation results (None/Exist Reference Genome).
```{r kegg_enrich_tree, warning=FALSE}
# 1. Load example datasets
data(kegg_anno)
# head(kegg_anno)

data(kegg_deg_fc)
# head(kegg_deg_fc)

# 2. Run kegg_enrich_tree analysis function
kegg_enrich_tree(
  kegg_anno,
  kegg_deg_fc,
  padjust_method = "fdr",
  pvalue_cutoff = 1,
  qvalue_cutoff = 1,
  sign_by = "p.adjust",
  category_num = 20,
  font_size = 4,
  low_color = "#ff0000aa",
  high_color = "#008888aa",
  hclust_method = "complete",
  ggTheme = "theme_light"
)
```

Get help using command `?TOmicsVis::kegg_enrich_tree` or reference page [https://benben-miao.github.io/TOmicsVis/reference/kegg_enrich_tree.html](https://benben-miao.github.io/TOmicsVis/reference/kegg_enrich_tree.html).
```{r}
# Get help with command in R console.
# ?TOmicsVis::kegg_enrich_tree
```

## 5.12 kegg_enrich_net
KEGG enrichment analysis and net plot based on KEGG annotation results (None/Exist Reference Genome).
```{r kegg_enrich_net, warning=FALSE}
# 1. Load example datasets
data(kegg_anno)
# head(kegg_anno)

data(kegg_deg_fc)
# head(kegg_deg_fc)

# 2. Run kegg_enrich_net analysis function
# kegg_enrich_net(
#   kegg_anno,
#   kegg_deg_fc,
#   padjust_method = "fdr",
#   pvalue_cutoff = 1,
#   qvalue_cutoff = 1,
#   category_num = 20,
#   net_layout = "circle",
#   net_circular = TRUE,
#   low_color = "#ff0000aa",
#   high_color = "#008888aa"
# )
```

Get help using command `?TOmicsVis::kegg_enrich_net` or reference page [https://benben-miao.github.io/TOmicsVis/reference/kegg_enrich_net.html](https://benben-miao.github.io/TOmicsVis/reference/kegg_enrich_net.html).
```{r}
# Get help with command in R console.
# ?TOmicsVis::kegg_enrich_net
```
