---
title: "SamplesStatistics"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{SamplesStatistics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# 1. Samples Statistics
## 1.1 quantile_plot
Quantile plot for visualizing data distribution.
```{r quantile_plot, warning=FALSE}
library(TOmicsVis)

# 1. Load box_data example datasets
data(quantile_data)

# 2. Run quantile_plot plot function
quantile_plot(
  quantile_data,
  my_shape = "fill_circle",
  point_size = 1.5,
  conf_int = TRUE,
  conf_level = 0.95,
  split_panel = "One_Panel",
  legend_pos = "right",
  legend_dir = "vertical",
  sci_fill_color = "Sci_AAAS",
  sci_color_alpha = 0.75,
  ggTheme = "theme_light"
)
```

Get help using command `?TOmicsVis::quantile_plot` or reference page [https://benben-miao.github.io/TOmicsVis/reference/quantile_plot.html](https://benben-miao.github.io/TOmicsVis/reference/quantile_plot.html).
```{r}
# Get help with command in R console.
# ?TOmicsVis::quantile_plot
```

## 1.2 corr_heatmap
Correlation Heatmap for samples/groups based on Pearson algorithm.
```{r corr_heatmap}
# 1. Load gene_exp example dataset
data(gene_exp)
head(gene_exp)

# 2. Run corr_heatmap plot function
corr_heatmap(
  gene_exp,
  corr_method = "pearson",
  cell_shape = "square",
  fill_type = "full",
  lable_size = 3,
  lable_digits = 3,
  color_low = "blue",
  color_mid = "white",
  color_high = "red",
  ggTheme = "theme_light"
)
```

Get help using command `?TOmicsVis::corr_heatmap` or reference page [https://benben-miao.github.io/TOmicsVis/reference/corr_heatmap.html](https://benben-miao.github.io/TOmicsVis/reference/corr_heatmap.html).
```{r}
# Get help with command in R console.
# ?TOmicsVis::corr_heatmap
```

## 1.3 pca_plot
PCA dimensional reduction visualization for RNA-Seq.
```{r pca_plot}
# 1. Load pca_sample_gene and pca_group_sample example datasets
data(pca_sample_gene)
data(pca_group_sample)

# 2. Run pca_plot plot function
pca_plot(
  pca_sample_gene,
  pca_group_sample,
  point_size = 5,
  text_size = 5,
  ellipse_alpha = 0.3,
  legend_pos = "right",
  legend_dir = "vertical",
  ggTheme = "theme_light"
)
```

Get help using command `?TOmicsVis::pca_plot` or reference page [https://benben-miao.github.io/TOmicsVis/reference/pca_plot.html](https://benben-miao.github.io/TOmicsVis/reference/pca_plot.html).
```{r}
# Get help with command in R console.
# ?TOmicsVis::pca_plot
```
