---
title: "TablesOperations"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{TablesOperations}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# 6. Tables Operations
## 6.1 table_split
Table split used for splitting a grouped column to multiple columns.
```{r table_split, warning=FALSE}
library(TOmicsVis)

# 1. Load table_split_data example datasets
data(table_split_data)
head(table_split_data)

# 2. Run table_split plot function
res <- table_split(table_split_data, 
                  grouped_var = "variable", 
                  miss_drop = TRUE
                  )
head(res)
```

Get help using command `?TOmicsVis::table_split` or reference page [https://benben-miao.github.io/TOmicsVis/reference/table_split.html](https://benben-miao.github.io/TOmicsVis/reference/table_split.html).
```{r}
# Get help with command in R console.
# ?TOmicsVis::table_split
```

## 6.2 table_merge
Table merge used to merge multiple variables to on variable.
```{r table_merge, warning=FALSE}
# 1. Load example datasets
data(table_merge_data)
head(table_merge_data)

# 2. Run function
res <- table_merge(
  table_merge_data,
  merge_vars = c("Ozone", "Solar.R", "Wind", "Temp"),
  new_var = "Variable",
  new_value = "Value",
  na_remove = FALSE
)
head(res)
```

Get help using command `?TOmicsVis::table_merge` or reference page [https://benben-miao.github.io/TOmicsVis/reference/table_merge.html](https://benben-miao.github.io/TOmicsVis/reference/table_merge.html).
```{r}
# Get help with command in R console.
# ?TOmicsVis::table_merge
```

## 6.3 table_filter
Table filter used to filter row by column condition.
```{r table_filter, warning=FALSE}
# 1. Load example datasets
data(table_filter_data)
head(table_filter_data)

# 2. Run function
res <- table_filter(table_filter_data, 
                    height > 100 & eye_color == "black"
                    )
head(res)
```

Get help using command `?TOmicsVis::table_filter` or reference page [https://benben-miao.github.io/TOmicsVis/reference/table_filter.html](https://benben-miao.github.io/TOmicsVis/reference/table_filter.html).
```{r}
# Get help with command in R console.
# ?TOmicsVis::table_filter
```

## 6.4 table_cross
Table cross used to cross search and merge results in two tables.
```{r table_cross, warning=FALSE}
# 1. Load example datasets
data(table_cross_data1)
head(table_cross_data1)

data(table_cross_data2)
head(table_cross_data2)

# 2. Run function
res <- table_cross(
  table_cross_data1,
  table_cross_data2,
  inter_var = "geneID",
  left_index = TRUE,
  right_index = FALSE
)
head(res)
```

Get help using command `?TOmicsVis::table_cross` or reference page [https://benben-miao.github.io/TOmicsVis/reference/table_cross.html](https://benben-miao.github.io/TOmicsVis/reference/table_cross.html).
```{r}
# Get help with command in R console.
# ?TOmicsVis::table_cross
```
