---
title: "TraitsAnalysis"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{TraitsAnalysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# 2. Traits Analysis
## 2.1 box_plot
Box plot support two levels and multiple groups with P value.
```{r box_plot, warning=FALSE}
library(TOmicsVis)

# 1. Load box_data example datasets
data(box_data)

# 2. Run box_plot plot function
box_plot(
  box_data,
  test_method = "wilcox.test",
  test_label = "p.format",
  notch = TRUE,
  group_level = "Three_Column",
  add_element = "dotplot",
  my_shape = "fill_circle",
  sci_fill_color = "Sci_AAAS",
  sci_fill_alpha = 0.5,
  sci_color_alpha = 1,
  legend_pos = "right",
  legend_dir = "vertical",
  ggTheme = "theme_light"
)
```

Get help using command `?TOmicsVis::box_plot` or reference page [https://benben-miao.github.io/TOmicsVis/reference/box_plot.html](https://benben-miao.github.io/TOmicsVis/reference/box_plot.html).
```{r}
# Get help with command in R console.
# ?TOmicsVis::box_plot
```

## 2.2 violin_plot
Violin plot support two levels and multiple groups with P value.
```{r violin_plot, warning=FALSE}
# 1. Load box_data example datasets
data(box_data)

# 2. Run violin_plot plot function
violin_plot(
  box_data,
  test_method = "wilcox.test",
  test_label = "p.format",
  group_level = "Three_Column",
  violin_orientation = "vertical",
  add_element = "boxplot",
  element_alpha = 0.5,
  my_shape = "plus_times",
  sci_fill_color = "Sci_AAAS",
  sci_fill_alpha = 0.5,
  sci_color_alpha = 1,
  legend_pos = "right",
  legend_dir = "vertical",
  ggTheme = "theme_light"
)
```

Get help using command `?TOmicsVis::violin_plot` or reference page [https://benben-miao.github.io/TOmicsVis/reference/violin_plot.html](https://benben-miao.github.io/TOmicsVis/reference/violin_plot.html).
```{r}
# Get help with command in R console.
# ?TOmicsVis::violin_plot
```

## 2.3 survival_plot
Survival plot for analyzing and visualizing survival data.
```{r survival_plot, warning=FALSE}
# 1. Load survival_plot example datasets
data(survival_data)

# 2. Run survival_plot plot function
survival_plot(
  survival_data,
  curve_function = "pct",
  conf_inter = TRUE,
  interval_style = "ribbon",
  risk_table = TRUE,
  num_censor = TRUE,
  sci_palette = "aaas",
  ggTheme = "theme_light",
  x_start = 0,
  y_start = 0,
  y_end = 100,
  x_break = 100,
  y_break = 25
)
```

Get help using command `?TOmicsVis::survival_plot` or reference page [https://benben-miao.github.io/TOmicsVis/reference/survival_plot.html](https://benben-miao.github.io/TOmicsVis/reference/survival_plot.html).
```{r}
# Get help with command in R console.
# ?TOmicsVis::survival_plot
```

## 2.4 tsne_plot
TSNE plot for analyzing and visualizing TSNE algorithm.
```{r tsne_plot, warning=FALSE}
# 1. Load tsne_plot example datasets
data(tsne_data)

# 2. Run tsne_plot plot function
tsne_plot(
  tsne_data,
  point_size = 3,
  point_alpha = 0.8,
  text_size = 2,
  text_alpha = 0.8,
  ci_level = 0.95,
  ellipse_alpha = 0.3,
  sci_fill_color = "Sci_AAAS",
  sci_color_alpha = 0.9,
  legend_pos = "right",
  legend_dir = "vertical",
  ggTheme = "theme_light"
)
```

Get help using command `?TOmicsVis::tsne_plot` or reference page [https://benben-miao.github.io/TOmicsVis/reference/tsne_plot.html](https://benben-miao.github.io/TOmicsVis/reference/tsne_plot.html).
```{r}
# Get help with command in R console.
# ?TOmicsVis::tsne_plot
```
